%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Anish Shanbhag} % Your name
\address{(+91)8971575068 \\ anishshanbhag15@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Objective} \itemsep -2pt
\item A budding Computer Science second-year undergraduate student looking for internship and skill 
\item development oppurtunities in the field of software development.
\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf BMS College Of Engineering} \hfill {\em 2016 - 2020 - Present} 
\\  Bachelor Of Computer Science and Engineering \hfill { Overall GPA:9.25/10 (till 4th Sem)}
\\ Bengaluru - India

{\bf V.V.S Sardar Patel PU College} \hfill {\em 2014-2016} 
\\  Higher Secondary Education \hfill {Percentage: 93.16 }
\\ Bengaluru - India
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}

\begin{rSubsection}{Internship, Perpule 1 Pay}{June 2018 - August 2018}{}
\item Developed a Angular5 web application called Video Walls for Sangeetha Mobiles which helps in video connection of customers in store and their best salesman in the headquarters.
\item Worked on the front-end design of Perpule Prime website.
\item Developed cordova plugins for Mosambee device of Perpule.
\end{rSubsection}

\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{ACADEMIC PROJECTS}

\begin{rSubsection}{BMSCE Marks Submission Portal}{Nov 2017}{}
\item An online application for students to view their marks.
\item Teachers/Admin uploads a CSV file containing marks of students in all subjects.
\item Students can view their marks by entering their college student number.
\item {\bf Technologies} : PHP , MySQL , Javascript , HTML5 , CSS3
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Shop Management System}{August 2017}{}{}
\item Designed to be implemented at any small-scale comapny/business,aiming at better organization and record keeping of details pertaining to the company.
 \item It keeps track of data such as product details , employee details etc which are vital for efficient functioning.
 \item {\bf Technologies} : C++
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages &  C/C++, Java , Python , Bash  \\
Web Development & HTML , CSS , Javascript , PHP , SQL  \\
Database & MySQL , mongoDB \\

\end{tabular}

\end{rSection}
\goodbreak

%----------------------------------------------------------------------------------------

\begin{rSection}{Courses Undertaken and Certifications}
\begin{rSubsection}{}{}{}{}
\item Database Management System , Data Structures , Data Communication , Operating System .
\item Completed requirements to be recognized as a Microsoft Technology Associate for Cloud Fundamentals.
\item Completed mongoDB for Java Developers course on MongoDB University.
\item Completed Bash Shell Scripting course on Udemy.
\item Completed JSP(Java Server Pages) and servlet course on Udemy. 
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------


\begin{rSection}{POSITION OF RESPONSIBILITY}

\begin{rSubsection}{Andriod App Devolpment Team of BMSCE UTSAV }{}{}{}
\item UTSAV is the cultural fest of BMS College Of Engineering .  It is one of the best fests in Karnataka.
\item The app has more than 1000 downloads.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular} \itemsep -3pt
\begin{rSubsection}{}{}{}{}
\item Secured 1st place in Indian Traditional Game- Lagori organised on occasion of National Youth Week Celebration-2017.
\item Secured 1st place in Pentagram (Maths Competion) held in Bengaluru.
\item 3rd Kyu(Brown Belt) in Okinawa Shorin - Ryu Karate-Do.
\end{rSubsection}
\end{rSection}

\end{document}
